Modelling Prehistoric Iconographic Compositions. The \proglang{R} package \pkg{iconr}

### 2020-12-18 article_rvTH17.Rnw
article

The notation of with nodes allows also to avoid, empirical and  top-down hierachical typologies . According to us, it is more convenient to record GUs (eg, an anthropomorph) and GUs varietes (an anthropomorph wearing an helmet) with different spatialized nodes (firstly within a GIS) rather than multiplying hierarchical levels of categories (e.g., a category of graphical units with \emph{n} types, a type with \emph{n} subtypes, a subtype with \emph{n} varieties, etc.) that lead also to tedious idiosynchratic inventories and difficult possible comparisons \emph{within} and \emph{between} these categories. For example, with the two types of GUs \code{casque} (helmet) and \code{personnage} (anthropomorphe) and the \emph{attribute} edge it is possible to describe: (1) a case where an anthropomorph wears a helmet (like for the Cerro Muriano steale, Figure \ref{fig:dec.1.4} left), (2) a case where an anthropomorph is separated from a helmet (like for the Zarza de Montanchez, Figure \ref{fig:dec.1.4} right). With a top-down hierachical typology, three types of GUs would have been required: (1) anthropomorph wearing a helmet (Cerro Muriano); (2) anthropomorph and (3) helmet (Zarza de Montanchez).

>>>>

The notation of with nodes allows also to avoid, empirical and  top-down hierachical typologies. According to us, it is more convenient to record GUs (eg, an anthropomorph) and GUs varietes (an anthropomorph wearing an helmet) with discrete spatialized nodes (firstly within a GIS) rather than multiplying a-spatial levels of hierarchical categories (e.g., a category of graphical units with \emph{n} types, a type with \emph{n} subtypes, a subtype with \emph{n} varieties, etc.) that lead also to tedious idiosynchratic inventories and difficult possible comparisons \emph{within} and \emph{between} these categories. For example, with the two types of GUs \code{casque} (helmet) and \code{personnage} (anthropomorphe) and the \emph{attribute} edge it is possible to describe: (1) a case where an anthropomorph wears a helmet (like for the Cerro Muriano steale, Figure \ref{fig:dec.1.4} left), (2) a case where an anthropomorph is separated from a helmet (like for the Zarza de Montanchez, Figure \ref{fig:dec.1.4} right). With a top-down hierachical typology, three types of GUs would have been required: (1) anthropomorph wearing a helmet (Cerro Muriano); (2) anthropomorph and (3) helmet (Zarza de Montanchez).
